Turbulence in compact to giant HII regions

### 2022-07-01 strucfunc_paper.tex
Javier updates 2022-06-29

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance} & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log S - (1.6 \pm 0.7)\).
The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the size determination is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

@@

This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.

>>>>

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The Figure \ref{fig:rvsR} shows the relation of the correlation length \(r_0\) and the diameter \(D\) of the region. 
The relationship we found is \(\log r_0 = (0.95 \pm 0.33) \log D - (1.6 \pm 0.7)\).
The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the size determination is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

@@

This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.
